Supplementary Material for the Paper ``Enriching Object Detection with\\2D-3D Registration and Continuous Viewpoint Estimation''

### 2014-11-21 experiments.tex
Supplementary material pdf
compressed

\begin{table}[!htbp]
  \footnotesize
  \setlength{\tabcolsep}{1pt}
  \centering
  \begin{tabular}{|c|c|r|c|r|}
    \hline
    Methods (AP/MPPE) & before calib.  & time & after calib.~\cite{Aubry14} & time \\
    \hline\hline
    HOG\cite{Dalal05}     & 72.3 / 65.0           &  31ms  & 60.4 / 50.2                 & 8.7 sec \\ 
    WHO\cite{Hariharan12} & 82.1 / 85.4           &  3811ms& 84.4 / 83.0                 & 12.4 sec  \\
    WHO-CG                & 81.7 / \textbf{84.9}  &  104ms & 83.7 / 87.3                 & 8.3 sec \\
    WHO-CG-Z              & 54.4 / 65.1           &  103ms & \textbf{92.8} / 86.7        & 8.7 sec  \\
    % NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
    NZ-WHO-CG {\em (ours)}  & \textbf{90.0} / 82.8  &   79ms & 90.3 / \textbf{86.8}        & 8.5 sec   \\
    \hline
  \end{tabular}
  \caption{Average Precision(AP), Mean Precision in Pose Estimation
    (MPPE)~\cite{Lopez-Sastre11}, and runtime for variations of WHO on
    3D Object Classes cars~\cite{Savarese07}. Please see text for
    details.}
  % WHO refers to standard WHO using the
  % method presented in \cite{Hariharan12}, WHO-CG uses iterative
  % Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the
  % whole template and zero out textureless region. NZ-WHO-CG is the
  % NZ-WHO which whitens only non-zero cells using iterative Conjugate
  % Gradient method. The time column indicates the time to generate one
  % template. We followed calibration procedure presented in \cite{Aubry14}.}
  \label{tab:who_initializations}
\end{table}

@@

We observe that our model performs on par with the state-of-the-art
methods in terms of AP ($99.8$) for cars. It performs slightly worse
on bicycles than DPM-VOC+VP ($93.0$ vs. $98.8$), but on par with the
ALM ($93.0$). In viewpoint estimation, our model performs slightly
worse than both methods ($91.7$ vs. $93.4$ and $97.5$ for cars, and
$87.4$ vs. $91.4$ and $97.5$ for bicycles, respectively).

@@

\begin{figure}[h]
    \begin{center}
    \setlength\tabcolsep{0pt}
\begin{tabular}{cc}
  \includegraphics[width=0.35\linewidth]{car_3dobject/7.png} &   
  \includegraphics[width=0.35\linewidth]{car_3dobject/8.png}\\ [-15pt]
%   (a) & (b) \\[0pt]
  \includegraphics[width=0.35\linewidth]{car_3dobject/11.png} &   
  \includegraphics[width=0.35\linewidth]{car_3dobject/12.png}\\ [-5pt]
%  (c) & (d) \\[0pt]
\end{tabular}
\end{center}
\caption{Detection results on 3D Object
  Classes~\cite{Savarese07}. Original image (left) and detection
  result overlaid on top (right).}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject}
\end{figure}

@@

\paragraph{Setup.}
We use detection bounding boxes provided by both object detectors and
augment it using our method to give viewpoint estimation. We use
detection bounding boxes from two different methods:
DPM-VOC+VP\cite{Pepik12} and R-CNN~\cite{Girshick14}, both in their
variants trained on 8 viewpoint categories, since these perform best
in terms of AP. For both methods,
we use the original score for plotting precision-recall curves
(meaning that we can not improve over their AP), but
enrich the detections with additional viewpoint information provided
by our method. For DPM-VOC+VP, we fall back to the viewpoint
estimation provided by this method in case the confidence of our
method falls below a threshold. For R-CNN, we fall back to a default
viewpoint prediction ($0$ angles).

>>>>

\begin{table}[!htbp]
  \footnotesize
  \setlength{\tabcolsep}{1pt}
  \centering
  \begin{tabular}{|c|c|r|c|r|}
    \hline
    Methods (AP/MPPE) & before calib.  & time & after calib.~\cite{Aubry14} & time \\
    \hline\hline
    HOG\cite{Dalal05}      & 72.3 / 65.0          &  31ms  & 60.4 / 50.2           & 8.7 sec \\ 
    WHO\cite{Hariharan12}  & 82.1 / \textbf{85.4} &  3811ms& 84.4 / 83.0           & 12.4 sec\\
    WHO-CG                 & 81.7 / 84.9          &  104ms & 83.7 / \textbf{87.3}  & 8.3 sec \\
    WHO-CG-Z               & 54.4 / 65.1          &  103ms & \textbf{92.8} / 86.7  & 8.7 sec \\
    % NZC-WHO-Z    & 89.10 /\textbf{78.64} &    & 91.15 / 74.79                  &     \\
    NZ-WHO-CG {\em (ours)} & \textbf{90.0} / 82.8 &   79ms & 90.3 / 86.8           & 8.5 sec \\
    \hline
  \end{tabular}
  \caption{Average Precision(AP), Mean Precision in Pose Estimation
    (MPPE)~\cite{Lopez-Sastre11}, and runtime for variations of WHO on
    3D Object Classes cars~\cite{Savarese07}. Please see text for
    details.}
  % WHO refers to standard WHO using the
  % method presented in \cite{Hariharan12}, WHO-CG uses iterative
  % Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the
  % whole template and zero out textureless region. NZ-WHO-CG is the
  % NZ-WHO which whitens only non-zero cells using iterative Conjugate
  % Gradient method. The time column indicates the time to generate one
  % template. We followed calibration procedure presented in \cite{Aubry14}.}
  \label{tab:who_initializations}
\end{table}

@@

We observe that our model performs on par with the state-of-the-art
methods in terms of AP ($99.8$) for cars. It performs slightly worse
on bicycles than DPM-VOC+VP ($93.0$ vs. $98.8$), but on par with the
ALM ($93.0$). In viewpoint estimation, our model performs slightly
worse than both methods ($91.7$ vs. $93.4$ and $97.5$ for cars, and
$90.9$ vs. $91.4$ and $97.5$ for bicycles, respectively).

@@

\begin{figure}[h]
    \begin{center}
    \setlength\tabcolsep{0pt}
\begin{tabular}{cc}
  \includegraphics[width=0.35\linewidth]{car_3dobject/7.png} &   
  \includegraphics[width=0.35\linewidth]{car_3dobject/8.png}\\ [-15pt]
%   (a) & (b) \\[0pt]
  \includegraphics[width=0.35\linewidth]{car_3dobject/11.png} &   
  \includegraphics[width=0.35\linewidth]{car_3dobject/12.png}\\ [-5pt]
%  (c) & (d) \\[0pt]
\end{tabular}
\end{center}
\caption{Detection results on 3D Object
  Classes~\cite{Savarese07}. Original image (left) and detection
  result overlaid on top (right).}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_vis}
\end{figure}

@@

\paragraph{Setup.}
We use detection bounding boxes provided by both object detectors and
augment it using our method to give viewpoint estimation. We use
detection bounding boxes from two different methods:
DPM-VOC+VP\cite{Pepik12} and R-CNN~\cite{Girshick14}, both in their
variants trained on 8 viewpoint categories, since these perform best
in terms of AP. For both cases,
we use the original score for plotting precision-recall curves
(meaning that we can not improve over their AP), but
enrich the detections with additional viewpoint information provided
by our method. We fall back to a default
viewpoint prediction ($0$ angles) in case the confidence of our
method falls below a threshold.
